---
title: "COVID19 in top 4 countries"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{COVID19 in top 4 countries}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = 'left'
)
```

```{r setup,warning=FALSE,message=FALSE}
library(COVID19top4)
library(tidyverse)
library(kableExtra)
```

This Package helps users in knowing the top 4 countries with the highest number of coronavirus cases throughout the world. The top 4 countries as of October 2020 are:

1. [United States of America](https://www.kaggle.com/sudalairajkumar/covid19-in-usa) 

1. [India](https://www.kaggle.com/sudalairajkumar/covid19-in-india) 

1. [Brazil](https://www.kaggle.com/unanimad/corona-virus-brazil)

1. [Russia](https://www.kaggle.com/kapral42/covid19-russia-regions-cases)

in order. This package has a shiny app which gives the analysis and visualizations for these countries throughout the COVID19 pandemic. The data for these analyses and visualizations are taken from the [COVID19 package](https://cran.r-project.org/package=COVID19) on CRAN and a couple of datasets from Kaggle for individual state datasets for each state within the country.These datasets all contain the total number of cases, deaths and recovered over time.

**NOTE!!** : Please click on the country for the link to these datasets.

## Some Examples on using the dataset within the package:

The table helps us find the total number of cases by country for each date.

```{r fig.width=5,fig.height=5}
corona %>% group_by(date, id) %>% 
  summarise(total = sum(confirmed)) %>% tail(10) %>% 
  knitr::kable() %>% kableExtra::kable_styling(bootstrap_options = "striped")
```

```{r warning=FALSE,fig.height=5,fig.width=5}
corona %>% 
  group_by(date,id) %>%
  summarise(total = sum(confirmed)) %>% 
  ggplot(aes(x = date, y = total,color =id))+
  geom_line()+ 
  facet_wrap(~id) +
  theme_minimal()
```

```{r warning=FALSE,fig.height=5,fig.width=5}
corona %>% group_by(date,id) %>% 
  summarise(school_closing = sum(school_closing)) %>% 
  ggplot(aes(x = date, y = school_closing, color = id))+
  geom_line()+
  facet_wrap(~id)+
  theme_minimal()
```


_The above examples are just a glimpse on how to use the datasets within this package, there are other datasets available for your exploration._
